OptiFit: a fast method for fitting amplicon sequences to existing OTUs

### 2021-06-24 paper/paper.Rmd
Roughhhh draft of figure for split strategy params

While we initially tested this strategy using an even split of the data into
reference and query fractions, we then wanted to investigate whether there was
an optimal reference fraction size.
To test the best reference size, reference sizes from 10% to 80% of the
sequences were created, with the remaining sequences used for the query.
OTU quality was remarkably stable across reference fraction sizes.
For example, splitting the human dataset 100 times yielded a coefficient of
variation of `r cv_fit_split_mcc_human_simple` for the MCC score across all
fractions.
Run time generally decreased as the reference fraction increased; for the human
dataset, the median run time was `r sec_fit_split_human_simple_1` with 10% of
sequences in the reference and `r sec_fit_split_human_simple_9` with 90% of
sequences in the reference.
In closed reference mode, the fraction of sequences that mapped increased as the
reference size increased; for the human dataset, the median fraction mapped was
`r frac_fit_split_human_simple_1` with 10% of sequences in the reference and 
`r frac_fit_split_human_simple_9` with 90% of sequences in the reference.
These trends hold for the other datasets as well (see supplemental figure **TODO**).
Thus, the reference fraction does not affect OTU quality in terms of MCC score,
but does affect the run time and the fraction of sequences that map during
closed reference mode.

>>>>

```{r results_split, fig.dim=figs('results_split', 'dim'), fig.cap=figs('results_split', 'cap')}
figs('results_split', 'path') %>% 
  tiff::readTIFF() %>% 
  grid::grid.raster() 
```

While we initially tested this strategy using an even split of the data into
reference and query fractions, we then wanted to investigate whether there was
an optimal reference fraction size.
To test the best reference size, reference sizes from 10% to 80% of the
sequences were created, with the remaining sequences used for the query.
OTU quality was remarkably stable across reference fraction sizes.
For example, splitting the human dataset 100 times yielded a coefficient of
variation of `r cv_fit_split_mcc_human_simple` for the MCC score across all
fractions.
Run time generally decreased as the reference fraction increased; for the human
dataset, the median run time was `r sec_fit_split_human_simple_1` with 10% of
sequences in the reference and `r sec_fit_split_human_simple_9` with 90% of
sequences in the reference (Figure \ref{fig:results_split}).
In closed reference mode, the fraction of sequences that mapped increased as the
reference size increased; for the human dataset, the median fraction mapped was
`r frac_fit_split_human_simple_1` with 10% of sequences in the reference and 
`r frac_fit_split_human_simple_9` with 90% of sequences in the reference.
These trends hold for the other datasets as well (see supplemental figure **TODO**).
Thus, the reference fraction does not affect OTU quality in terms of MCC score,
but does affect the run time and the fraction of sequences that map during
closed reference mode.
